Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-23 article.tex
wording

Low frequencies of the signal correspond to the the slow
decay of fluorescence, while communication between neurons are
characterized by short delay. The second step of our pipeline consists in
identifying neuron spikes -- of high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}

>>>>

Neurons communicates through short peaks, characterized by a high
frequency, while low frequencies of the signal corresponds to the slow
decay of fluorescence. The second step of our pipeline consists in
identifying neuron spikes by filtering out
low frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}
